---
title: 'Entity Recognition Assignment'
author: "Yueze Xu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
#do not change this
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/hera-/Desktop/HU/ANLY520/HW")
```

## Libraries / R Setup

- In this section, include the *R* set up for Python to run. 

```{r warning=FALSE}
##r chunk
library(reticulate)
py_config()
library(wordnet)
setDict("C:/Program Files (x86)/WordNet/2.1/dict")
```

- In this section, include import functions to load the packages you will use for Python.

```{python}
##python chunk
import warnings
warnings.filterwarnings('ignore')
from nltk.corpus import wordnet as wn
import pandas as pd
from nltk.corpus import wordnet_ic
import spacy
from spacy.util import minibatch, compounding
from pathlib import Path
import random
```

## Synsets

- You should create a Pandas dataframe of the synsets for a random word in Wordnet.
- Use https://www.randomword.net/ to find your random word.
- You should create this dataframe like the example shown for "fruit" in the notes.

```{python}
##python chunk
#Choose 'season' as my word
season_sets_py = wn.synsets("season")
print(season_sets_py)
season_df = pd.DataFrame([
  {"Synset": each_synset, 
  "Part of Speech": each_synset.pos(), 
  "Definition": each_synset.definition(), 
  "Lemmas": each_synset.lemma_names(), 
  "Examples": each_synset.examples()} 
  for each_synset in season_sets_py])
season_df
season_df["Definition"]
```

## Nyms

- Include the hymonyms and hypernyms of the random word from above. 

```{python}
##python chunk
season= season_sets_py[0]
#Homonyms:a subordinate name, more specific 
season.hyponyms()
#Hypernyms: a superordinate name, more abstract
season.hypernyms()
```

## Similarity

- Think of two related words to your random word. You can use the synonyms on the random generator page. Calculate the JCN and LIN similarity of your random word and these two words. (four numbers total).

```{python}
##python chunk
#word 1: temper
temper = wn.synsets("temper")
temper[0].definition()
temper = temper[0]

#word 2: Spring
spring = wn.synsets("Spring")
spring[0].definition()
spring = spring[0]

#JCN
semcor_ic = wordnet_ic.ic('ic-semcor.dat')

print('Season vs Temper(JCN similarity): ', season.jcn_similarity(temper, semcor_ic))
print('Season vs Spring(JCN similarity): ', season.jcn_similarity(spring, semcor_ic))
#LIN
print('Season vs Temper(LIN similarity): ', season.lin_similarity(temper, semcor_ic))
print('Season vs Spring(LIN similarity): ', season.lin_similarity(spring, semcor_ic))
```

## NER Tagging

- Create a blank spacy model to create your NER tagger. 

```{python}
##python chunk
nlp = spacy.load('en_core_web_sm')  # load existing spacy model
nlp = spacy.blank('en')  # create blank Language class

```

- Add the NER pipe to your blank model. 

```{python}
##python chunk
ner = nlp.create_pipe('ner')
nlp.add_pipe(ner, last=True)
```

- Create training data. 
  - Go to: http://trumptwitterarchive.com/
  - Note you can pick other people than Trump by using "Additional Accounts" at the top right. 
  - Create training data with at least 5 tweets. 
  - Tag those tweets with PERSON, LOCATION, GPE, etc. 

```{python}
##python chunk
training_data = [
  (u"Why didn’t Bill Barr reveal the truth to the public, before the Election, about Hunter Biden. Joe was lying on the debate stage that nothing was wrong, or going on - Press confirmed. Big disadvantage for Republicans at the polls!",
   {'entities': [ (11,19,'PERSON'),(80,96,'PERSON') ]}),
  
  (u"No candidate has ever won both Florida and Ohio and lost. I won them both, by a lot! #SupremeCourt",
   {'entities': [(31,37,'LOCATION'),(43,46,'LOCATION')]}),
  
  (u"Thank you and congratulations to General Flynn. He and his incredible family have suffered greatly! https://t.co/UjH6LVuON8",
   {'entities': [(33,45,'PERSON'),(100,122,'URL')]}),
   
  (u"FOR COURAGE & BRILLIANCE! https://t.co/mPM5ejy2lU",
   {'entities': [(26,48,'URL')]}),
   
  (u"Big Rally Saturday Night in Georgia!!!",
   {'entities': [(28,34,'LOCATION')]})
]

```

- Add the labels that you used above to your NER tagger. 

```{python}
##python chunk
nlp.entity.add_label('PERSON')
nlp.entity.add_label('LOCATION')
nlp.entity.add_label('URL')
```

- Train your NER tagger with the training dataset you created. 

```{python}
##python chunk
optimizer = nlp.begin_training()

#run through training
for i in range(20):
  random.shuffle(training_data)
  for text, annotations in training_data:
    nlp.update([text], [annotations], sgd=optimizer)
```

## Using your NER Tagger 

- Use one new tweet from the same writer you had before. 
- Use your new NER tagger to see if it grabs any of the entities you included. 
***Did not get it, the model may need further modification***
```{python}
##python chunk
new_tweet = nlp(u'Manufacturers are being held back by the strong Dollar, which is being propped up by the ridiculous policies of the Federal Reserve - Which has called interest rates and quantitative tightening wrong from the first days of Jay Powell')

print("Entities", [(ent.text, ent.label_) for ent in new_tweet.ents])
```

